\documentclass{beamer}

% markidis
% rev 1.2 

\usetheme{dresden}

\title{Math Regulations\\~Mathematical and Procedural Analysis}
\author{Suela Xhanaj\\
      Marco Matteo Markidis}
\date{\today}



\begin{document}

% 1
\begin{frame}
\section{Overview} %%%
	\maketitle
\end{frame}

\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}

% 2a
\begin{frame}
\frametitle{Regulated Markets}
\begin{itemize}
\item<1-> Regulated markets, in economics and particularly in finance[,] are financial markets characterized\emph {by the presence of regulations} on market organization, i.e., operations, listing requirements, requirements for becoming intermediaries, and trading rules. [Wikipedia]
\item<2-> Regulated markets (as opposed to over-the-counter markets) are subject to specific and stringent rules[.] [Wikipedia]
\end{itemize}
\end{frame}

% 2b
\begin{frame}
\frametitle{Regulated Markets: remote gambling}
\begin{itemize}
\item<1-> Guidelines for regulating \emph{remote gambling};
\item<2-> mathematical analysis;
\item<3-> source code analysis;
\item<4-> gameplay and verification procedures.
\item<5-> client requirements, gaming platforms, RNG, ...
\end{itemize}
\end{frame}

% 2b
\begin{frame}
\frametitle{Unregulated markets: remote gambling}
\begin{itemize}
\item<1-> Undisciplined markets;
\item<2-> deep--web;
\item<3-> cryptocurrencies?
\item<4-> minimum RTP ?
\item<5-> protective for the player?
\item<6-> RNG without security requirements?
\end{itemize}
\end{frame}

% 2c
\begin{frame}
\frametitle{Remote gambling}
The control of gambling is reserved for the state, which has exercised it through AAMS (Autonomous Administration of State Monopolies) since 2000. The Administration entrusts the operation of gambling to private entities, which must provide the necessary investments and suitable entrepreneurial tools and manage the gambling according to rules. Compliance with these rules is constantly verified to protect the public. Italian legislation aims to consider remote gambling as a form of entertainment and socialization, substantially differentiating it from other games based primarily on individual behaviors and a distance, both physical and temporal, between the moment of gambling and that of winning.[ ADM Website]
\end{frame}

% 2d
\begin{frame}
\frametitle{Accreditation}
\begin{itemize}
\item<1-> 31 accreditations: IT, UK, ..., LOTBA, Panama, Mendoza,BR-PR ...
\item<2-> accreditation ISO17025 (UK, MT, SE, DK, GR, ON,BG);
\item<3-> accreditation ISO17020 (NL);
\item<4-> GLI--19;
\end{itemize}
\end{frame}

% 3
\begin{frame}
\frametitle{Useful Material}
\begin{itemize}
\item<1-> Regulations: Nexcloud Malta$\backslash$Jurisdictions,updated by Compliance Manager;
\item<2-> Certification Matrix -- Math : Nextcloud Italia$\backslash$Parma$\backslash$\_Utilities, updated by Chief Mathematician Officer (CMO);
\item<3-> Additional Procedure : Github, aggiornato da CMO.
\item<4-> MathTraining.pdf : Nextcloud Italia$\backslash$Parma$\backslash$\_Documentation$\backslash$Formazione, updated by CMO;
\end{itemize}
\end{frame}

% 4
\begin{frame}
\frametitle{Regulations}
\begin{itemize}
\item<1-> Official Reference;
\item<2-> in the original language: IT italiano, UK inglese, EE?
\item<3-> Contain references to all regulations.
\item<4-> Technical guideline (UK);
\item<5-> Updates (LOTBA, CH) and replacements (NL).
\end{itemize}
\end{frame}

% 5
\begin{frame}
\frametitle{Certification Matrix -- Math}
\begin{itemize}
\item<1-> Item matrix - regulations;
\item<2-> Internal operational tool;
\item<3-> easy visualization;
\item<4-> in progress and in definition: easy finding.
\end{itemize}
\end{frame}

% 6
\begin{frame}
\frametitle{Procedure}
\begin{itemize}
\item<1-> Additional tools \emph{required} by regulations for verification:
\item<2-> Live RTP Monitoring, checksum tool, ...;
\item<3-> or \emph{regulated} in gaming: jackpot, gamble, ..
\end{itemize}
\end{frame}

%7
\begin{frame}
\section{Data under certification} %%%
\centering \Large Mathematical Analysis \\ \large Data under certification
\end{frame}

% 8
\begin{frame}
\frametitle{Data under certification}
\begin{itemize}
\item<1-> \emph{RTP} : all regulations;
\item<2-> \emph{Standard deviation} : Live RTP Monitoring and Console ADM;
\item<3-> \emph{Hit rate} : Console ADM;
\item<4-> \emph{Max win} : specific requirements;
\item<5-> \emph{Win celebration} : specific requirements.
\end{itemize}
\end{frame}

% 9
\begin{frame}
\frametitle{Minimum RTP}
\begin{itemize}
\item<1-> IT: 90\% for slots, 80\% tournaments, 70\% bingo;
\item<2-> MT: 85\%;
\item<3-> LOTBA :90\%.
\end{itemize}
\end{frame}

% 10
\begin{frame}
\frametitle{Max Win}
\begin{itemize}
\item<1-> Two requirements:
\item<2-> Monetary Max Win : CZ, GR, ...
\item<3-> Inclusion in the report: CH.
\end{itemize}
\end{frame}

% 11
\begin{frame}
\frametitle{Max Bet}
\begin{itemize}
\item<1-> CZ: 1000 CZK;
\item<2-> GR: 20 euro;
\item<3-> UI Requirements!
\item<4-> Max Win GR: 140000 euro...
\item<5-> ...Max Win x Bet?
\end{itemize}
\end{frame}

% 12
\begin{frame}
\frametitle{Win celebration}
\begin{itemize}
\item<1-> UI Requirements;
\item<2-> regulation: UK, ON;
\item<3-> to check with UI team!
\end{itemize}
\end{frame}

% 13
\begin{frame}
\frametitle{Buy Feature}
Two requirements:
\begin{itemize}
\item<2-> not allowed: UK, NL;
\item<3-> allowed only in some cases: LT.
\item<4-> ...and Ultra Bet?
\end{itemize}
\end{frame}

% 14
\begin{frame}
\section{Technical Requirements}
\centering \Large Mathematical Analysis \\ \large Technical Requirements
\end{frame}

% 15a
\begin{frame}
\frametitle{Inadmissibility of Adaptive Behavior in Games}
A player using a game proposed as based on a random event must have equal chances of obtaining any possible combination in each game (subject to the provisions of the game rules). It is therefore inadmissible, in the case of fixed-odds games of chance and card games organized in a form other than a tournament, for the RTP to be manipulated by the system or manually to keep it constant.
\end{frame}

% 15b
\begin{frame}
\frametitle{Adaptivity}
\begin{itemize}
\item<1-> Probabilities that change in a non-transparent manner for the player;
\item<2-> Compensatory mechanism.
\item<3-> Not allowed in all regulations;
\item<4-> Some have a \emph{strong} point: IT..
\item<5-> Easy finding!
\end{itemize}
\end{frame}

% 16a
\begin{frame}
\frametitle{Metamorphosis}
\begin{itemize}
\item<1-> A spin is dependent on the previous one (spins have memory!);
\item<2-> The triad of metamorphosis: UI requirements
\item<3-> bet level, progress bar, rules!
\item<4-> Transparent to the player.
\item<5-> Not allowed for: CZ, CH. But...
\end{itemize}
\end{frame}

% 16b
\begin{frame}
\frametitle{Metamorphosis CH: a "but" story}
\begin{itemize}
\item<1-> Article 7 OMJ: The results of the game shall be determined only by invariant parameters. Any mechanisms such as a \emph{compensator} or \emph{regulator} are forbidden. [The game results must be determined solely by invariant parameters. Any mechanism such as a \emph{compensator} or \emph{regulator} is prohibited.]
\item<2-> \emph{compensator} : Adaptive behavior not allowed.
\item<3-> \emph{regulator} : Metamorphic behavior not allowed... if it occurs "quantitatively"!
\item<4-> Evaluation of metamorphic RTP.
\item<5-> Games with metamorphic scenarios certifiable (certified!) for CH.
\end{itemize}
\end{frame}

% 16c
\begin{frame}
\frametitle{Metamorphosis CZ: a "non--but" story}
\begin{itemize}
\item<1->Article 50.1 Zak 2016-186: A technical game spin is a \emph{completed} process during which, as a result of one its triggering, a random process of the game result is generated and a bet wagered for one spin is subtracted from the deposit at the latest before the game is closed.
\item<2-> \emph{completed} : Adaptive and metamorphic behavior not allowed.
\item<3-> No mines games, no tower games, ...
\end{itemize}
\end{frame}

% 17
\begin{frame}
\frametitle{Ultra Bet}
\begin{itemize}
\item<1-> Not allowed "consequently".
\item<2-> Regulator mechanism \emph{always} present...
\item<3-> ...5 games from a client..
\end{itemize}
\end{frame}

% 18
\begin{frame}
\frametitle{Paid Respin}
\begin{itemize}
\item<1-> Possibility to lock some reels and \emph{buy} the spin in this configuration.
\item<2-> The respin must be paid.
\item<3-> Not allowed in CH: "the result [...] must be determined solely by invariant parameters.".
\item<4-> Information Letter 2020: "games that offer variable betting options depedending on the result of previous games cannot be accepted. An example are games with a so called respin-mechanism. For an additional bet, players are offered a second chance to improve their results by spinning any desider reel again while the others remain locked."
\end{itemize}
\end{frame}

% 19
\begin{frame}
\section{Game Procedure}
\centering \Large Mathematical Analysis \\ \large Game Procedure
\end{frame}

% 20
\begin{frame}
\frametitle{Jackpot}
\begin{itemize}
\item<1-> Reference Regulations: IT.
\item<2-> Two fundamental points:
\item<3-> A.1.3: All players contributing to the progressive jackpot must be able to win it while participating in the game.
\item<4-> A.1.4: In order to ensure the fairness of the game, i) the probability of winning the progressive jackpot must be directly proportional to its contribution, or ii) the amount of the progressive jackpot paid to the player must be directly proportional to its contribution.
\end{itemize}
\end{frame}

% 21
\begin{frame}
\frametitle{Gamble}
\begin{itemize}
\item<1-> Reference Regulations: GR.
\item<2-> Two requirements:
\item<3-> it must be fair (i.e. RTP = 100\%) (math requirement);
\item<4-> The player must be able to decide whether to participate or not (UI requirement).
\end{itemize}
\end{frame}

% 22
\begin{frame}
\section{Verification Procedure}
\centering \Large Mathematical Analysis \\ \large Verification Procedure
\end{frame}

% 21
\begin{frame}
\frametitle{Live RTP Monitoring}
\begin{itemize}
\item<1-> Periodic RTP Verification Tool In-Game.
\item<2-> Regulations: UK, SE, ON, LOTBA, ES, CO, CH.
\item<3-> Reference Regulations: UK (e LOTBA).
\item<4-> Technical guideline vs. Regulations;
\item<5-> live RTP Monitoring vs. internal diagnosis system.
\end{itemize}
\end{frame}

% 22
\begin{frame}
\frametitle{Certification Materials}
\begin{itemize}
\item<1-> Source Code for Automated Procedures (i.e., Queries for Data Extraction and Database Export).
\item<2-> Documentation: Failure Handling, Procedure Description.
\item<3-> Simulation: For each game, simulated RTP, standard deviation, and number of simulations required.
\item<3-> Internal Tools: AdditionalProcedure (for required materials) and Certification Matrix - Math (for regulations).
\end{itemize}
\end{frame}

% 23
\begin{frame}
\frametitle{Checksum Tool}
\begin{itemize}
\item<1-> Periodic Verification Tool for Critical File Signatures and Potential Exposure.
\item<2-> Regulations: IT, SE, LT, ON, LOTBA.
\item<3-> Reference Regulations: IT.
\item<4-> Verification of Critical Components and Exposure vs. Monitoring System.
\end{itemize}
\end{frame}

% 24
\begin{frame}
\frametitle{2.2.7 Security}
% inserisco la normativa
%1. Lo SGAD deve prevedere: \\
1.1. Automatic verification procedures, to be executed at least daily, for the integrity of gaming components and the RNG, and any software involved in generating symbols or game combinations, [...] including the software responsible for calculating and sending message digests of each verified file/module/function to the control system. These automatic verification procedures must involve the daily calculation of the hash of critical software determined by the ODV, using the SHA1 or MD5 hashing algorithm. The calculated result must be verified by the ODV during testing and sent to ADM according to the communication protocol.\\
1.2. Execution of blocking procedures in response to events signaling malfunctions and/or attempted tampering of gaming components and the RNG.
\end{frame}

% 25
\begin{frame}
\frametitle{Certification Materials}
\begin{itemize}
\item<1-> Source Code: database (query and table), configuration file, folder searching
\item<2-> Documentation: errors handling, logging procedure, how and when the tool is run.
\item<3-> Internal Tools: AdditionalProcedure (for required materials) e Certification matrix -- Math (for regulation).

\end{itemize}
\end{frame}

% 25
\begin{frame}
\frametitle{Control Program}
\begin{itemize}
\item<1-> Establish a method for verifying each component of the control program..
\item<2-> Regulations: GLI - 19,Mendoza,PE.
\item<3-> Independent Third-Party Verification of system security software.
\item<4-> Approval by the authority for the integrity verification method before system approval .
\end{itemize}
\end{frame}

% 26
\begin{frame}
\section{Additional Points}
\centering \Large Mathematical Analysis \\ \large Additional Points
\end{frame}

% 27
\begin{frame}
\frametitle{Public Strategy}
\begin{itemize}
\item<1-> Skill games employ a \emph{perfect} strategy to achieve an \emph{optimal} RTP..
\item<2-> Some regulations explicitly state that the strategy must be:
\item<3-> either documented in literature (see "standard" Blackjack);
\item<4-> or provided in the rules (see "non-standard" Blackjack).
\end{itemize}
\end{frame}

% 28a
\begin{frame}
\frametitle{Identification of Critical Files}
\begin{itemize}
\item<1-> Critical File: A file whose integrity is necessary for compliance with regulations.
\item<2-> RES-TEC, 4.1 Critical components: Critical components are those parts that must have enhanced security since they have a significant role in the realisation of the gambling activity [LOTBA, RESDI-2019-80, Articulo 59].
\item<3-> PT: Hardware, software or other components required to be present and operational in order for the online gambling system to operate properly.
\end{itemize}
\end{frame}

% 28b
\begin{frame}
\frametitle{Supervised Build}
\begin{itemize}
\item<1->IT, 1.2.2.1: Source Code: The certified source code and the compiled code in production must be provenly identical. The ODV, upon completion of the verification process, will send to ADM the message digests of each verified file/module/function deemed critical by the ODV itself for the correct execution of the gaming phases, with reference to the hardware and/or software components related to the RNG and any software involved in generating game symbols and combinations.
\end{itemize}
\end{frame}

% 28b
\begin{frame}
\frametitle{Supervised Build}
\begin{itemize}
\item<1->PE,Mendoza : Log Information Requirement.
\item<1->Additional information about the logs of the source code is required to ensure the verification process covers all aspects.
\end{itemize}
\end{frame}

% 28c
\begin{frame}
\frametitle{File ADM, IT 1.2.2.1}
In addition, the following documents will be sent:
\begin{itemize}
\item<1->  text file containing the full absolute PATH name and the SHA1 message digest [...] of the individual source files delivered and other necessary software components;
\item<1-> the compilation log also containing the SHA1 message digests [...] of the compiled source files, and the timestamp and SHA1 message digest [...] of the log itself;
\end{itemize}
\end{frame}

% 28d
\begin{frame}
\frametitle{File ADM, IT 1.2.2.1}
\begin{itemize}
\item<1-> a text file containing the full absolute PATH name and the SHA1 message digest [...] of all critical binary files installed on each component of the remote gaming platform, including the games. If the compilation generates archives containing multiple files, the individual files, not the archives, must be included in the aforementioned file;
\item<1-> the script necessary to generate the files mentioned in the previous point and the SHA1 or MD5 message digest of the script.
\end{itemize}
\end{frame}

% ultima
\begin{frame}
\frametitle{References}
\begin{itemize}
\item<1-> Metamorphic Scenario Games: iSoftbet -- Sea of Riches (CH), Leander -- Red Hot Reels.
\item<1-> Ultra Bet: iSoftbet -- Pyramid Pays, Book of Sheba, Legend of the Four Beasts, Book of Cai Shen, Hot Shots 2 .
\item<1-> Paid Respin: Nolimit City -- Book of Shadows.
\item<1-> Gamble: iSoftbet - Majestic Gold Megaways.
\item<1-> Public Strategy: Evolution - Lightning Blackjack DK.
\item<1-> Buy Feature LT: 1x2 - Astro Newts Megaways.
\item<1-> Detailed Max Win in the report: Gamanza - Cherry Deluxe 10000.
\end{itemize}
\end{frame}

% ultima
\begin{frame}
\frametitle{References}
\begin{itemize}
\item<1-> Adaptivity: PSMTEC - Montezuma, Giocaonline - Al bar dello Sport, Playson - Juice Inc.
\item<1-> Metamorphosis: Tom Horn - Frutopia, GameArt - Sushi Yatta.
\item<1-> Mines game: iSoftbet - Aztec Gold Mines.
\item<1-> Tower game: iSoftbet - Rise of the Genie (o Rasputin!, di Boney M. :)
\end{itemize}
\end{frame}

\end{document}